\LARGE How coexistence mechanisms mediate temporal stability

### 2014-10-21 modelNotes.Rnw
little update to text

\begin{align}
\frac{\text{d}D_{i}}{\text{d}t} &= c_{i}b_{i}(N_{i} + g_{i,e}D_{i}) - m_{D,i}D_{i}\\
\frac{\text{d}N_{i}}{\text{d}t} &= f(R)(N_{i} + g_{i,e}D_{i}) - c_{i}b_{i}(N_{i} + g_{i,e}D_{i})  - m_{N,i}(N_{i}+g_{i,e}D_{i})\\
\frac{\text{d}R_{i}}{\text{d}t} &= a(S - R) - \sum\limits_{i=1,2}f(R)(N_{i}+g_{i,e}D_{i})
\end{align}
where $i$ denotes species, $D$ is the dormant (long-lived) biomass state, $B$ is the living biomass (fast-growing, shorter-lived) state, $b$ is the ``birth" rate of new biomass in the dormant state, $c$ is some factor related to the cost of producing the dormant state, and $m$s are biomass loss rates. $g$ is a time-fluctuating activation rate of dormant biomass to the live biomass state that occurs at discrete times $e$ (in our case, every `year'). The growth rate of living biomass is a resource-dependent function, $f(R) = r_{i}R/(K_{i}+R)$, where $r$ is the maximum growth rate and $K$ is the resource level at which growth is one-half $r$. For the resource dynamics, whose state is denoted by $R$, we use a linear resource renewal equation where $a$ scales resource turnover rate and $S$ is the resource equilibrium when consumers are absent, and an offtake of the resource equal to the sum of each species' consumption, $\sum_{i=1,2}f(R)(N_{i}+g_{i,e}D_{i})$. If $g_{1,2}=1$ across all $e$ events then $D$ and $N$ collapse into one state and we have a basic consumer-resource model of two species competiting for one essential resource.

>>>>

\begin{align}
\frac{\text{d}D_{i}}{\text{d}t} &= c_{i}b_{i}(N_{i} + g_{i,e}D_{i}) - m_{D,i}D_{i}\\
\frac{\text{d}N_{i}}{\text{d}t} &= f(R)(N_{i} + g_{i,e}D_{i}) - c_{i}b_{i}(N_{i} + g_{i,e}D_{i})  - m_{N,i}(N_{i}+g_{i,e}D_{i})\\
\frac{\text{d}R_{i}}{\text{d}t} &= a(S - R) - \sum\limits_{i=1,2}f(R)(N_{i}+g_{i,e}D_{i})
\end{align}
where $i$ denotes species, $D$ is the dormant (long-lived) biomass state, $N$ is the living biomass (fast-growing, shorter-lived) state, $b$ is the ``storage" rate of live biomass to the dormant state, $c$ is some factor related to the cost of producing the dormant state, and $m$s are biomass loss rates. $g$ is a time-fluctuating activation rate of dormant biomass to the live biomass state that occurs at discrete times $e$ (in our case, every `year'). The growth rate of living biomass is a resource-dependent function, $f(R) = r_{i}R/(K_{i}+R)$, where $r$ is the maximum growth rate and $K$ is the resource level at which growth is one-half $r$. For the resource dynamics, whose state is denoted by $R$, we use a linear resource renewal equation where $a$ scales resource turnover rate and $S$ is the resource equilibrium when consumers are absent, and an offtake of the resource equal to the sum of each species' consumption, $\sum_{i=1,2}f(R)(N_{i}+g_{i,e}D_{i})$. If $g_{1,2}=1$ across all $e$ events then $D$ and $N$ collapse into one state and we have a basic consumer-resource model of two species competiting for one essential resource.
